### 2021-04-27 input/related_work.tex
10 pages + typos

Content indexing services in geo-distributed infrastructures allow
\processes to retrieve specific content while leveraging the
advantages of replication. These systems mostly rely on dedicated
location services host by possibly remote third-party \processes; and
cutting out the middleman requires that each \process maintains its
own index in a decentralized fashion.
% This section reviews these
% approaches.

@@

\noindent A central server that registers both these
information~\cite{snamp, p2p-oracle, fogstore, p2p-alto} facilitates
the computation, for it gathers all knowledge in one place. However,
it comes with well-known issues inherent to its distribution paradigm
such as load balancing, or single point of failure.
%% Numerous solutions
%% maintain an index of all replica locations on a centralized
%% server. This comes with well-known disadvantages inherent to
%% centralized solutions such as load balancing, robustness or locality
%% that are even magnified in an Edge context.

@@

Cutting out the middleman by hosting a location service on each and
every \process improves response time of content retrieval. However,
it still requires every \process to index every live replica as well
as their respective distance in order to rank them.
%% The opposite approach consists in hosting the index directly on the
%% nodes, avoiding any prior request to access a content.
\underline{N}amed \underline{D}ata \underline{N}etworking
(NDN)~\cite{nlsr} broadcasts information about cache updates to all
\nodes in the system. Having the entire knowledge of all the replica
locations along with distance information carried into messages, each
\node easily determine where the closest copy of specific content
resides, without contacting any remote
service. \underline{C}onflict-\underline{f}ree \underline{r}eplicated
\underline{d}atatype (CRDT)~\cite{shapiro2011crdts} for set data
structures could also implement such a location service. \Processes
would eventually have a set of all replicas, assuming eventual
delivery of messages.
\noindent Such solutions inherently imply that every \process receives
every message, which contradicts with the principles of Edge
infrastructures that aim at reducing the volume of data passing
through the network. On the opposite, each \process running \NAME only
registers its closest replica. This allows \NAME to use scoped
broadcast as a communication primitive to lock down the traffic
generated by content indexing based on distances.
% Such solutions inherently imply that every node will
% eventually receive all messages, contrary to \NAME.

@@

Some state-of-the-art approaches also confine the dissemination of
information to interested \processes based on distance. 
% \item [Membership protocols:]

@@

\noindent The most closely related approaches to \NAME come from
\underline{i}nformation-\underline{c}entric \underline{n}etworking
(ICN)~\cite{garcia-lopez, hemmati2015namebased}. They periodically
advertise their cache content, and advertisements stop as soon as they
reach uninterested \processes. However their operation requires that
\begin{inparaenum}[(i)]
\item they constantly generate traffic even in quiescent systems where
  \processes do not add nor destroy replicas; and 
\item they define physical-clock-based timeouts the value of which
  depends on network topology properties such as network diameter.
  %also incur an overhead even in quiet contexts without any update.
  % Moreover, they necessarily rely on physical timeouts
  Unfitting timeouts lead to premature removals of live replicas; or
  slow convergence where \processes wrongly believe that their closest
  replica is live while it was destroyed.
\end{inparaenum}
On the opposite, \NAME quickly inform each \process of their closest
replica even in large networks; and when the system becomes quiescent,
\NAME has no overhead.

>>>>

Content indexing services in geo-distributed infrastructures allow
\processes to retrieve specific content while leveraging the
advantages of replication. These systems mostly rely on dedicated
location services host by possibly remote third-party \processes; but
cutting out the middleman requires that each \process maintains its
own index in a decentralized fashion.
% This section reviews these
% approaches.

@@

\noindent A central server that registers both these information
facilitates the computation, for it gathers all knowledge in one
place~\cite{snamp, p2p-oracle, fogstore, p2p-alto}. However, it comes with
well-known issues such as load balancing, or single point of failure.
%% Numerous solutions
%% maintain an index of all replica locations on a centralized
%% server. This comes with well-known disadvantages inherent to
%% centralized solutions such as load balancing, robustness or locality
%% that are even magnified in an Edge context.

@@

Cutting out the middleman by hosting a location service on each and
every \process improves response time of content retrieval. However,
it still requires every \process to index every live replica as well
as their respective distance in order to rank them.
%% The opposite approach consists in hosting the index directly on the
%% nodes, avoiding any prior request to access a content.
\underline{N}amed \underline{D}ata \underline{N}etworking
(NDN)~\cite{nlsr} broadcasts information about cache updates to all
\nodes in the system. Having the entire knowledge of all the replica
locations along with distance information carried into messages, each
\node easily determine where the closest copy of specific content
resides, without contacting any remote
service. \underline{C}onflict-\underline{f}ree \underline{r}eplicated
\underline{d}atatype (CRDT)~\cite{shapiro2011crdts} for set data
structures could also implement such a location service. \Processes
would eventually have a set of all replicas, assuming eventual
delivery of messages.
\noindent Such solutions imply that every \process receives every
message, which contradicts with the principles of Edge infrastructures
that aim at reducing the volume of data passing through the
network. On the opposite, each \process running \NAME only registers
its closest replica. This allows \NAME to use scoped broadcast as a
communication primitive to lock down the traffic generated by content
indexing based on distances.
% Such solutions inherently imply that every node will
% eventually receive all messages, contrary to \NAME.

@@

Some state-of-the-art approaches confine the dissemination of messages
to interested \processes too.
% \item [Membership protocols:]

@@

\noindent The most closely related approaches to \NAME come from
\underline{i}nformation-\underline{c}entric \underline{n}etworking
(ICN)~\cite{garcia-lopez, hemmati2015namebased}. They periodically
advertise their cache content, and advertisements stop as soon as they
reach uninterested \processes. However their operation requires that
\begin{inparaenum}[(i)]
\item they constantly generate traffic even in quiescent systems where
  \processes do not add nor destroy replicas; and 
\item they define physical-clock-based timeouts the value of which
  depends on network topology properties such as network diameter.
  %also incur an overhead even in quiet contexts without any update.
  % Moreover, they necessarily rely on physical timeouts
  Unfitting timeouts lead to premature removals of live replicas; or
  slow convergence where \processes wrongly believe that their closest
  replica is live while it was destroyed.
\end{inparaenum}
On the opposite, \NAME quickly informs each \process of its closest
replica even in large networks; and when the system becomes quiescent,
\NAME has no overhead.
